TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-01-19 article.tex
Paper TTT: revisando un poco m'as la introducci'on

    \edge {d} {r};
    \edge {p1,p2} {d};
    \edge {s1} {p1};
    \edge {s2} {p2};
    %\node[invisible, right=of p2, xshift=4.35cm] (s-dist) {};
}
     \caption{
     \en{Generative model in which skills cause the observable results mediated by the difference of hidden performances, $d =p_i - p_j$, both random variables around their unknown true skill, $p \sim \N(s,\beta^2)$.}
    \es{Modelo generativo en el que las habilidades causan los resultados observables a trav\'es de la diferencia de rendimientos ocultos, $d=p_i-p_j$, ambas variables aleatorias centradas en la verdadera habilidad, $p \sim \N(s,\beta^2)$}
    %
    \en{The one with the highest performance wins, $r = (d > 0)$.}
    \es{Gana quien haya obtenido mayor rendimiento, $r = (d > 0)$.}
    %
    \en{Observable variables are painted gray, hidden in white, and constants are shown as black dots.}
    \es{Las variables observables se pintan de gris, la ocultas en blanco, y las constantes se muestran como puntos negros.}
    }
    \label{fig:generative_model}
\end{figure}
%
\en{Figure~\ref{fig:generative_model} provides a causal model in which skills generates the observable result.}
\es{La figura~\ref{fig:generative_model} ofrece un modelo causal en la que las habilidades generan el resultado observable.}
%
\en{The agents exhibit different performances at each event, varying around their true skill, $\N(p_i\,|\,s_i,\beta^2)$.}
\es{Los agentes exhiben distintos desempe\~nos en cada evento, que var\'ian alrededor de su verdadera habilidad, $\N(p\,|\,s,\beta^2)$.}
%
\en{The variance $\beta^2$ only serves as a scale: skills separated by a distance equivalent to a $\beta$ always have a 76\% probability of winning.}
\es{La varianza $\beta^2$ s\'olo sirve como escala: habilidades separada por un $\beta$ siempre tienen una probabilidad de ganar de 76\%.}
%
\en{The model assumes that the agent with the highest performance wins, $r = (p_i > p_j)$. In other words, whoever obtains a difference of performance greater than 0 wins, $r = (p_i - p_j > 0)$.}
\es{El modelo supone que gana el agente con mayor rendimiento, $r = (p_i > p_j)$, o en otras palabras, gana quien obtenga una diferencia de rendimiento mayor a 0, $r = (p_i - p_j > 0)$.}

@@

\en{Using the graphical representation it is possible to derive the prediction of the result given the previous estimates, $P(\,r\,|\,s_{i_\text{old}},s_{j_\text{old}}\,)$.}

@@

\en{Elo's methodological solution is simple and smart: update both previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, based on the surprise (i.e. the complement of the prediction of the observed result).}

@@

\en{where the probability arises from instantiating the previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, in the generative model (details in section~\ref{sec:exactSolution}).}

@@

\en{The idea is that the magnitud of the surprise $\Delta$ is related to how accurate the previous estimates are, and therefore can be used to update them.}

@@

\en{Because new agents start with arbitrary estimates (the same initial value is used for all individuals), they tend to generate greater surprise values and abruptly modify estimates that had already converged.}

@@

\en{Instead of selecting a single value as an estimate, a superior alternative consists on distributing the certainty among all possible skill hypotheses.}

@@

\en{The \ref{eq:bayes_theorem} allows to optimally update our beliefs about the hypotheses, given a model and the data.}

@@

\en{The prior quantifies the previous uncertainty, and the posterior reduces it based on the information provided by the data, given the model.}

@@

\en{The likelihood and the evidence are both probabilities about the observed result, so they can be seen as predictions (since the results are discrete variables, those probabilities are written with capital letters).}

@@

\en{As an instance, let's consider a winning case ($p_i > p_j$) using Gaussian priors, $\N(\,s\,|\,\mu, \sigma^2)$.}

@@

\en{As we observed that the agent $i$ won, we know from the causal model that the hidden difference of performances was indeed positive.}

@@

\en{Since the evidence is constante, the posterior uncertainty of each hypothesis is proportional to the product of their prior uncertainty and their likelihood, as shown in equation~\ref{eq:posterior_win}.}

@@

\en{In section~\ref{sec:exactSolution} we will see in detail how all this equations arises by applying the sum and product rule over the model.}

@@

\en{It is important to stress that the posterior, although similar, is not a Gaussian distribution, preventing us from using the equation~\ref{eq:posterior_win}  iteratively.}
\es{Es importante remarcar que la posterior, aunque se parezca, no es una distribuci\'on Gaussiana, lo que nos impedir\'a usar la ecuaci\'on~\ref{eq:posterior_win} iterativamente.}
%
\en{But due the shape of the exact posterior, a Gaussian seem to be a good enough approximation, allowing us to avoid the computational cost of the sampling methodologies.}
\es{Por la forma del posterior exacto, una Gaussiana parece una aproximaci\'on suficientemente buena, que nos permitir\'ia evitar el costo computacional de las metodolog\'ias de sampleo.}
%
\en{The main contribution of the Glicko system~\citep{glikman_gliko_2} was the development of an efficient method to approximate the exact posterior with a Gasussian distribution.}
\es{El principal aporte del sistema Glicko~\citep{glikman_gliko_2} fue el desarroll\'o de un m\'etodo eficiente para aproximar la posterior exacta con una distribuci\'on Gasussiana.}
%
\en{However, this offers no guarantee that the selected Gaussian is the one that best approximates it.}
\es{Sin embargo, esta no ofrece garant\'ias de que la Gaussiana seleccionada sea la que mejor aproxima.}
%
\en{The success of the TrueSkill solution~\citep{Herbrich2007} is based on the application of an efficient method for computing the Gaussian that best approximates the exact posterior (section~\ref{sec:approximate_posterior}).}
\es{El \'exito de la soluci\'on TrueSkill~\citep{Herbrich2007} se basa en la aplicaci\'on de m\'etodo eficiente para calcular la Gaussiana que mejor aproxima a la posterior exacta (secci\'on~\ref{sec:approximate_posterior}).}
%
\begin{equation} \label{eq:approx} 
 \widehat{p}(s_i| r, s_j) = \underset{\mu, \sigma}{\text{ arg min }} \ \ \text{KL}(\, p(s_i| r, s_j) \, || \,  \N(s_i|\mu, \sigma^2) \, )
\end{equation}
%
\en{This kind of methods, which minimize the Kullback-Leibler divergence between the true and the approximate distribution, allows to perform Bayesian inference in situations that otherwise would be impossible.}
\es{Esta clase de m\'etodos, que minizan la divergencia Kullback-Leibler entre la distribuci\'on verdadera y aproximada, permiten realizar Inferencia Bayesiana en situaciones que de otra forma no ser\'ia posibles.}
%
\en{In our case, in which we need to know how skills change over time, this technique allow us to efficiently apply the equation~\ref{eq:posterior_win} iteratively over a sequence of observations.}
\es{En nuestro caso, en el que necesitamos conocer c\'omo cambian las habilidades a trav\'es del tiempo, est\'a t\'ecnica nos permite aplicar eficientemente la ecuaci\'on~\ref{eq:posterior_win} iterativamente sobre una secuencia de observaciones.}

>>>>

    \edge {d} {r};
    \edge {p1,p2} {d};
    \edge {s1} {p1};
    \edge {s2} {p2};
    %\node[invisible, right=of p2, xshift=4.35cm] (s-dist) {};
}
     \caption{
     \en{Generative model in which skills cause the observable results mediated by the difference of hidden performances, $d =p_i - p_j$, both random variables around their unknown true skill, $p \sim \N(s,\beta^2)$.}
    \es{Modelo generativo en el que las habilidades causan los resultados observables a trav\'es de la diferencia de rendimientos ocultos, $d=p_i-p_j$, ambas variables aleatorias centradas en la verdadera habilidad, $p \sim \N(s,\beta^2)$}
    %
    \en{The one with the highest performance wins, $r = (d > 0)$.}
    \es{Gana quien haya obtenido mayor rendimiento, $r = (d > 0)$.}
    %
    \en{Observable variables are painted gray, hidden in white, and constants are shown as black dots.}
    \es{Las variables observables se pintan de gris, la ocultas en blanco, y las constantes se muestran como puntos negros.}
    }
    \label{fig:generative_model}
\end{figure}
%
\en{Figure~\ref{fig:generative_model} provides a causal model in which skills generates the observable result.}
\es{La figura~\ref{fig:generative_model} ofrece un modelo causal en la que las habilidades generan el resultado observable.}
%
\en{The agents exhibit different performances at each event, varying around their true skill, $\N(p_i\,|\,s_i,\beta^2)$.}
\es{Los agentes exhiben distintos desempe\~nos en cada evento, que var\'ian alrededor de su verdadera habilidad, $\N(p\,|\,s,\beta^2)$.}
%
%
\en{The model assumes that the agent with the highest performance wins, $r = (p_i > p_j)$. In other words, whoever obtains a difference of performance greater than 0 wins, $r = (p_i - p_j > 0)$.}
\es{El modelo supone que gana el agente con mayor rendimiento, $r = (p_i > p_j)$, o en otras palabras, gana quien obtenga una diferencia de rendimiento mayor a 0, $r = (p_i - p_j > 0)$.}
\en{The parameter $\beta^2$ is used as a global scale for the model.}
\es{La varianza $\beta^2$ s\'olo sirve como escala: habilidades separada por un $\beta$ siempre tienen una probabilidad de ganar de 76\%.}

@@

\en{Using the graphical representation proposed in Fig.~\ref{fig:generative_model}, it is possible to derive the prediction of the result given the previous estimates, $P(\,r\,|\,s_{i_\text{old}},s_{j_\text{old}}\,)$.}

@@

\en{Elo's methodological solution is simple and smart: updates both previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, based on the surprise (i.e. the complement of the prediction of the observed result).}

@@

\en{where the probability arises from instantiating the previous estimates, $s_{i_\text{old}}$ and $s_{j_\text{old}}$, in the generative model (more details in section~\ref{sec:exactSolution}).}

@@

\en{The idea is that the magnitude of the surprise $\Delta$ is related to the accuracy of the previous estimates and, therefore, can be used to update them.}

@@

\en{Because new agents start with arbitrary skills (the same initial value is used for all individuals), they tend to generate greater surprise values and abruptly modify estimates that had already converged.}

@@

\en{Instead of selecting a single value as an estimate, an enhancement consists of distributing the certainty among all possible skill hypotheses.}

@@

\en{The \ref{eq:bayes_theorem} allows us to optimally update our beliefs about the hypotheses, given a model and the data.}

@@

\en{The prior quantifies the uncertainty about the known player's skill and the posterior decreases this uncertainty based on the information provided by the data (i.e. the result) and the given the model.}

@@

\en{The likelihood and the evidence are both probabilities of the observed result, so they can be seen as predictions (since the results are discrete variables, those probabilities are expressed using capital letters).}

@@

\en{As an instance, let's consider a winning case ($p_i > p_j$) using a Gaussian prior (i.e. $\N(\,s\,|\,\mu, \sigma^2)$) for each of the skill estimations.}

@@

\en{As we observed that the agent $i$ won, we know from the causal model that the hidden difference of performances was, indeed, positive.}

@@

\en{Since the evidence is a constant value, the posterior uncertainty of each hypothesis is proportional to the product of their prior uncertainty and their likelihood, as shown in equation~\ref{eq:posterior_win}.}

@@

\en{Section~\ref{sec:exactSolution} shows how these equations arise by applying the sum and product rule over the model.}

@@

\en{It is important to stress that the posterior, although similar, is not a Gaussian distribution, preventing us from using equation~\ref{eq:posterior_win} iteratively.}
\es{Es importante remarcar que la posterior, aunque se parezca, no es una distribuci\'on Gaussiana, lo que nos impedir\'a usar la ecuaci\'on~\ref{eq:posterior_win} iterativamente.}
%
\en{But due to the shape of the exact posterior, a Gaussian distribution could be used as a good approximation, allowing us to avoid the computational cost of the sampling methodologies.}
\es{Por la forma del posterior exacto, una Gaussiana parece una aproximaci\'on suficientemente buena, que nos permitir\'ia evitar el costo computacional de las metodolog\'ias de sampleo.}
%
\en{The main contribution of the Glicko system~\citep{glikman_gliko_2} was the development of an efficient method to approximate the exact posterior using a Gaussian distribution.}
\es{El principal aporte del sistema Glicko~\citep{glikman_gliko_2} fue el desarroll\'o de un m\'etodo eficiente para aproximar la posterior exacta con una distribuci\'on Gasussiana.}
%
\en{However, this method does not guarantee the quality of the approximation used.}
\es{Sin embargo, esta no ofrece garant\'ias de que la Gaussiana seleccionada sea la que mejor aproxima.}
%
\en{The success of the TrueSkill solution~\citep{Herbrich2007} is based on the application of an efficient method for computing the Gaussian distribution that best approximates the exact posterior (section~\ref{sec:approximate_posterior}).}
\es{El \'exito de la soluci\'on TrueSkill~\citep{Herbrich2007} se basa en la aplicaci\'on de m\'etodo eficiente para calcular la Gaussiana que mejor aproxima a la posterior exacta (secci\'on~\ref{sec:approximate_posterior}).}
%
\begin{equation} \label{eq:approx} 
 \widehat{p}(s_i| r, s_j) = \underset{\mu, \sigma}{\text{ arg min }} \ \ \text{KL}(\, p(s_i| r, s_j) \, || \,  \N(s_i|\mu, \sigma^2) \, )
\end{equation}
%
\en{This kind of methods, which minimize the Kullback-Leibler divergence between the true and the approximate distribution, allows to perform Bayesian inference in situations that otherwise would be impossible.}
\es{Esta clase de m\'etodos, que minizan la divergencia Kullback-Leibler entre la distribuci\'on verdadera y aproximada, permiten realizar Inferencia Bayesiana en situaciones que de otra forma no ser\'ia posibles.}
%
\en{In our case, in which we need to know how skills change over time, this technique allows us to efficiently apply the equation~\ref{eq:posterior_win} iteratively over a sequence of observations.}
\es{En nuestro caso, en el que necesitamos conocer c\'omo cambian las habilidades a trav\'es del tiempo, est\'a t\'ecnica nos permite aplicar eficientemente la ecuaci\'on~\ref{eq:posterior_win} iterativamente sobre una secuencia de observaciones.}
